On the Dynamics of Anthropomorphism in Robotics \thanks{This research was supported by the Swiss National Science Foundation through the National Centre of Competence in Research Robotics.}

### 2013-05-22 anthropomorphism.tex
Completed my biography

\textbf{Julia Fink} is a PhD student in Human-Robot Interaction at EPFL. Her work focusses on the analysis of interaction, user experience and acceptance of robots in domestic spaces. She has a multi-disciplinary background in Media, Technology, Communication, and Interaction Studies. \\

\textbf{Dr. S\'{e}verin Lemaignan} is a postdoctoral researcher at EPFL. ...  \\

>>>>

\textbf{Julia Fink} is a PhD student in Human-Robot Interaction at EPFL. Her
work focuses on the analysis of interaction, user experience and acceptance of
robots in domestic spaces. She has a multi-disciplinary background in Media,
Technology, Communication, and Interaction Studies. \\

\textbf{Dr. Séverin Lemaignan} is a postdoctoral researcher at EPFL. His work
focuses on robotics and its application to education and learning, with an
emphasis on human-robot interaction. He obtained in 2012 a PhD from the
CNRS/LAAS (France) and the Technical University of Munich (Germany) in
cognitive robotics, and has a background both in mechanical engineering and
education sciences.\\
